---
title: "A3: SPL Library Checkouts"
output: html_document
---

### Introduction

The data used in this report is collected by the Seattle Public Library and it records every item checked out in from the beginning of 2022 to the end of January in 2023. This report will analyze various information ranging from authors, to genre, to material type. The data visualization on authors is a line graph comparing the numbers of checkouts per month for the Taylor Jenkins Reid and Colleen Hoover. These authors were chosen as they had books which were gained huge popularity this past year despite being published in 2016/2017. For Taylor Jenkins Reid, that book was "The Seven Husbands of Evelyn Hugo" and for Colleen Hugo, that book was "It Ends with Us." The next data visualization displays the numbers of checkouts per month for three popular genres. This includes romance, thriller, and mystery. These genres were chosen because I have a personal interest in all three and thought they would be the most popular. The last data visualization will be a bar chart which displays the number of checkouts by material type for books in different forms, videos and audios. This includes physical books, audio books, e-books, video discs, and audio discs. 

### Summary Information

Write a summary paragraph of findings that includes the 5 values calculated from your summary information R script

These will likely be calculated using your DPLYR skills, answering questions such as:

- What is the average number of checkouts for each item?
- What is the month or year with the most/least checkouts for a book that you're interested in?
- What is the month or year with the most/least checkouts for ebooks?
- How has the number of print book checkouts changed over time?

Feel free to calculate and report values that you find relevant.

### The Dataset

- Who collected/published the data?  
- What are the parameters of the data (dates, number of checkouts, kinds of books, etc.)?
- How was the data collected or generated?  
- Why was the data collected?  
- What, if any, ethical questions do you need to consider when working with this data?  
- What are possible limitations or problems with this data?   (at least 200 words)


### First Trends Over Time Chart

Include a chart. Make sure to describe why you included the chart, and what patterns emerged

The first chart that you will create and include will show the trend over time of your variable/topic/interest. Think carefully about what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- Show more than one, but fewer than ~10 trends
  - For example, two books, or 5 different mediums
- You must have clear x and y axis labels
- The chart needs a clear title
- You need a legend for your different line colors and a clear - legend title
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

When we say "clear" or "human readable" titles and labels, that means that you should not just display the variable name.

Here's an example of how to run an R script inside an RMarkdown file:

```{r linechart1, fig.width=12}
source('chart1_example.R')
ch_tjr_graph
```

### Second Trends Over Time Chart

Include a chart. Make sure to describe why you included the chart, and what patterns emerged

The second chart that you will create and include will show another trend over time of your variable/topic/interest. Think carefully about what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- Show more than one, but fewer than ~10 trends
  - For example, two books, or 5 different mediums
- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear - legend title
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

When we say "clear" or "human readable" titles and labels, that means that you should not just display the variable name.

Here's an example of how to run an R script inside an RMarkdown file:

```{r linechart2, fig.width=12}
source('chart2_example.R')
genre_graph
```

### Your Choice

The last chart is up to you. It could be a line plot, scatter plot, histogram, bar plot, stacked bar plot, and more. Here are some requirements to help guide your design:

- You must have clear x and y axis labels
- The chart needs a clear title
- You need a legend for your different line colors and a clear legend title

Here's an example of how to run an R script inside an RMarkdown file:

```{r barchart, fig.width=12}
source('chart3_example.R')
bar_chart
```


